---
author: Mikayla Kerchen
date: '`r format(Sys.Date())`'
title: RMarkdown Lab Part 2
output:
  prettydoc::html_pretty:
    theme: hpstr
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.path = "../Output/")
```

# Load Libraries
```{r}
library(tidyverse)
library(here)
library(prettydoc)
library(kableExtra)
```

# Load Data

I am loading chemical data from Maunalua, HI. 
```{r}
ChemData <- read.csv(here("Week_06", "Data", "chemicaldata_maunalua.csv"))  # Loads in the data

```

# Inspecting the Data

I am making sure the data was imported properly.
```{r}
glimpse(ChemData)     # Allows me to view a glimpse of the data
```

# Plotting Data 

This plot represents the *Temperature* plotted against the *Salinity*. They are grouped by the **Season** they were measured in.

```{r, fig.align='center', fig.cap= "Figure 1: A violin plot comparing temperature and salinity based on the season they were measured."}
ChemData %>%
  ggplot(aes(x = Temp_in,           # Makes a plot of Temperature and Salinity grouped by Season
             y = Salinity,
             fill = Season))+
  geom_violin()+                    # Makes a violin plot
  facet_wrap(~Season)+              # Wraps the data according to season
  labs(x = "Temperature",            # Adds pretty names to my plot
       y = "Salinity",
       title = "Temperature vs. Salinity",
       subtitle = "Based on Season")+
  theme_bw()+
  theme(axis.title = element_text(size = 12,             # Changes the size, color, face, and horizontal adjustment of the plot
                                  color = "black"),
        plot.title = element_text(size = 14,
                                  color = "black",
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 12,
                                     color = "black",
                                     face = "italic",
                                     hjust = 0.5))+
  scale_fill_viridis_d()                               # Uses the viridis color pallete 

```

# Making a Table

I will create a table for the data using:

* Mean temperature
* Mean salinity
* Tide_time

```{r}
ChemData%>%
  group_by(Tide_time) %>%     # Groups data by Tide_time
  summarize(mean_temp = mean(Temp_in, na.rm = TRUE),           # Calculates the mean of the temperature and salinity
            mean_salinity = mean(Salinity, na.rm = TRUE)) %>%
  kbl(col.names = c("Tide_Time", "Mean Temperature", "Mean Salinity")) %>% # Makes it a kable table and adds column names
  kable_classic() %>%     # Changes the theme of the table
  row_spec(0, bold = T, color = "white", background = "#008080") %>%   # Changes the text, font, color, and background
  kable_styling(full_width = FALSE)
```


