---
title: "Independent Project"
subtitle: "Comparison of Cat and Dog Owners Across the United States"
author: "Mikayla Kerchen"
institute: "CSUN"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Load Libraries

```{r, message=FALSE}
library(tidyverse)
library(here)
library(usmap)
library(reshape2)
```

---

# Introduction to the Data Set

- The data was received from the Tidy Tuesday Repository

--

- The data frame includes cat and dog owner data from the United States

--

```{r}
CatvDog_Data <- read.csv(here("Independent Project", "Data", "cats_vs_dogs.csv"))
```
---

# Cat Owner Percentage in the United States

- This is the code I used to make the plot on the next slide.

--

```{r CatPercentPlot, eval= FALSE, message=FALSE}
plot_usmap(data = CatvDog_Data,           
           values = "percent_cat_owners",  
           regions = "states",
           exclude = c("AK", "HI"),       
           color = "black")+
  labs(title = "Cat Owners of the United States",         
       subtitle = "Percentage of Cat Owners by State")+
  theme(panel.background = element_blank(),             
        legend.position = "right")+
  scale_fill_continuous(low = "white", high = "blue", name = "Percentage of Cat Owners")
```


---

# Cat Owner Percentage in the United States

- The plot below displays the percentage of cat owners per state in the United States.

--

- It only includes the continental states due to lacking data from Alaska and Hawaii.

--

.center[
```{r CatPercentPlot-out, ref.label="CatPercentPlot", echo=FALSE, message=FALSE, warning=FALSE, out.width= '500'}
```
]

---

# Dog Owner Percentage in the United States

- This is the code I used to make the plot on the next slide.

--

```{r DogPercentPlot, eval= FALSE, message=FALSE}
plot_usmap(data = CatvDog_Data,           # Plots a flat map of the US.
           values = "percent_dog_owners",  # Uses the data set and plots the percentage data.
           regions = "states",
           exclude = c("AK", "HI"),       # Excluding Alaska and Hawaii from the map since there is no data for them.
           color = "black")+
  labs(title = "Dog Owners of the United States",         # Adds titles to the plot.
       subtitle = "Percentage of Dog Owners by State")+
  theme(panel.background = element_blank(),             # Makes the map blank inside and put the legend to the right.
        legend.position = "right")+
  scale_fill_continuous(low = "white", high = "red", name = "Percentage of Dog Owners")    # Gives a gradient effect in order of how high or low the percentage is.
```

---

# Dog Owner Percentage in the United States

- The plot below displays the percentage of dog owners per state in the United States.

--

- Like the plot before, this only contains the continental states due to lacking data from Alaska and Hawaii.

--

.center[
```{r DogPercentPlot-out, ref.label="DogPercentPlot", echo=FALSE, message=FALSE, warning=FALSE, out.width= '500'}
```
]

---

# Comparing Number of Dog and Cat Households by State

```{r, echo=FALSE}
CatvDog_Data_Bar <- melt(CatvDog_Data[,c('state', 'n_dog_households', 'n_cat_households')], id.vars = 1)
```


```{r}
CatvDog_Data_Bar %>%
  ggplot(aes(x = state,
             y = value))+
  geom_bar(aes(fill = variable), stat = "identity", position = "dodge")+
  scale_y_log10()+
  coord_flip()
```

