---
title: "Independent Project"
subtitle: "Comparison of Cat and Dog Owners Across the United States"
author: "Mikayla Kerchen"
institute: "BIOL 551"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

# Load Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(usmap)
library(reshape2)
```

---

# Introduction to the Data Set

- The data was received from the Tidy Tuesday Repository

--

- The data frame includes cat and dog owner data from the United States

--

```{r}
CatvDog_Data <- read.csv(here("Independent Project", "Data", "cats_vs_dogs.csv"))
```
---

# Cat Owner Percentage in the U.S.

- This plot illustrates the percentage of cat owners in the United States.

--

- This plot only contains data for the continental states due to lacking data for Alaska and Hawaii.

--
.pull-left[
```{r CatPercentPlot, eval= FALSE, message=FALSE}
plot_usmap(data = CatvDog_Data,           
           values = "percent_cat_owners",  
           regions = "states",
           exclude = c("AK", "HI"),       
           color = "black")+
  labs(title = "Cat Owners of the United States",         
       subtitle = "Percentage of Cat Owners by State")+
  theme(panel.background = element_blank(),             
        legend.position = "right")+
  scale_fill_continuous(low = "white", high = "blue", name = "Percentage of Cat Owners")
```
]
.pull-right[
```{r CatPercentPlot-out, ref.label="CatPercentPlot", echo=FALSE, message=FALSE, warning=FALSE}
```
]
---

# Dog Owner Percentage in the U.S.

- This plot illustrates the percentage of dog owners in the United States.

--

- Like the plot before, this plot only contains data for the continental states due to lacking data for Alaska and Hawaii.

--

.pull-left[
```{r DogPercentPlot, eval= FALSE, message=FALSE}
plot_usmap(data = CatvDog_Data,           # Plots a flat map of the US.
           values = "percent_dog_owners",  # Uses the data set and plots the percentage data.
           regions = "states",
           exclude = c("AK", "HI"),       # Excluding Alaska and Hawaii from the map since there is no data for them.
           color = "black")+
  labs(title = "Dog Owners of the United States",         # Adds titles to the plot.
       subtitle = "Percentage of Dog Owners by State")+
  theme(panel.background = element_blank(),             # Makes the map blank inside and put the legend to the right.
        legend.position = "right")+
  scale_fill_continuous(low = "white", high = "red", name = "Percentage of Dog Owners")    # Gives a gradient effect in order of how high or low the percentage is.
```
]
.pull.right[
```{r DogPercentPlot-out, ref.label="DogPercentPlot", echo=FALSE, message=FALSE, warning=FALSE}
```
]

---

# Dog and Cat Households by State

- This next plot is a bar plot that compares the number of dog and cat households per state.

--

- I ordered this plot from the larger amount of dog and cat households to the lowest.

```{r, echo=FALSE}
CatvDog_Data_Bar <- melt(CatvDog_Data[,c('state', 'n_dog_households', 'n_cat_households')], id.vars = 1)
```

---

# Dog and Cat Households by State

.pull-left[
```{r CatvDogBar, eval=FALSE, message=FALSE}
CatvDog_Data_Bar %>%     
  ggplot(aes(x = reorder(state, value), # Reorders the plot from most to least value
             y = value))+
  geom_bar(aes(fill = variable), stat = "identity", position = "dodge")+
  scale_y_log10()+  # Scales the y-axis by log10
  coord_flip()+   # Flips the coordinate plane
  labs(x = "State",   # Gives pretty labels to the plot
       y = "Number of Households",
       fill = "Type of Household",
       title = "Comparison of Number of Dog and Cat Households in the U.S.",
       subtitle = "Categorized per State")+
  scale_fill_discrete(labels = c('Dog Household', 'Cat Household'))+   # Re-labels the legend with prettier names (ex: instead of 'n_dog_households' and 'n_cat_households')
  theme_bw()+   # Standard black and white theme.
  theme(plot.title = element_text(size = 16,     # Changes the size, color, face, and adjusts the title and subtitle.
                                  color = "black",
                                  face = 'bold',
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 14,
                                     color = "black",
                                     face = 'italic',
                                     hjust = 0.5),
        axis.title = element_text(size = 12,      # Chnages the size and color of the axis and legend titles.
                                  color = "black"),
        legend.title = element_text(size = 12,
                                    color = "black"))
```
]

.pull-right[
```{r CatvDogBar-out, ref.label="CatvDogBar", echo=FALSE, message=FALSE, warning=FALSE}
```
]

---

# Dog and Cat Households by State

- As expected, the states with larger populations have the larger amount of both dog and cat households.

--

  - This could have to do with some states having a specific amount of dogs and cats that each household can have.

--

  - Usually goes by county.

--

- From the plot, it appears that more household have dogs compared to cats.

--

  - Except for a few states: 

--

  - Massachusetts
    
--

  - Connecticut

--

  - Maine

--

  - and some other mainly east coast states
  
--
---

# Statistics for Dogs vs. Cats

```{r}
CatvDog_Data_Stats <- CatvDog_Data %>%
  mutate(mean_cat_population = mean(cat_population),
         mean_dog_population = mean(dog_population),
         avg_dogs_per_household = mean(avg_dogs_per_household),
         avg_cats_per_household = mean(avg_cats_per_household))
```


