---
title: "Good Plot/Bad Plot"
author: "Mikayla Kerchen"
date: "`r Sys.Date()`"
output: 
   prettydoc::html_pretty:
    theme: cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

## Load Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(gganimate)
library(ggimage)
library(magick)
```

## Load Data

```{r}
# Read in the data from Tidy Tuesday repository
Honey_Data <- read.csv(here("Good Plot & Bad Plot", "Data", "honeyproduction.csv"))

glimpse(Honey_Data)
```

## Bad plot

```{r echo=TRUE, results='hide'}
Honey_Data %>%
  ggplot(aes(x = priceperlb,   
            y = yieldpercol,
            fill = year)) + 
  geom_col()+                 # Makes a column plot
  labs(title = "honey prod.")+         # Adds a title
  scale_fill_gradient(low = "yellow", high = "#ac8405")+   # Editing the colors of the gradient 
  theme(panel.background = element_rect(fill = "#43382f"),   # Edits the colors of the plot
        plot.background = element_rect(fill = "#43382f"),
        axis.title.x = element_text(color = "#ac8405"),
        axis.title.y = element_text(color = "#ac8405"),
        axis.text = element_text(color = "yellow"),
        plot.title = element_text(color = "#ac8405"))
```

```{r, message=FALSE}
ggsave(here("Good Plot & Bad Plot", "Output", "BeePlot.png"))
# Saves the image of the bad plot
 
bee <- image_read(here("Good Plot & Bad Plot","Output","Bee.png"))
# Adding image of Barry from Bee Movie

beeplot<-image_read(here("Good Plot & Bad Plot","Output","BeePlot.png"))
beeout <- image_composite(beeplot, bee, offset = "+950+450")
beeout 
# Combined the plot image and the image of Barry
```

## What Makes the Bad Plot so **bad**?

* No visible story to tell with the data
* Too many bars that are unable to be differentiated from one another
* No neat labels
* An image that doesn't add anything to the plot
* Unnecessary colors that distract the viewer from the plot
* Legend is not very useful when columns are not easily visible


## Good Plot

```{r}
Honey_Data %>%
  mutate(numcol = numcol/1000) %>%  # Divided the number of colonys by 1000
  ggplot(aes(x = yieldpercol,   
             y = priceperlb,
             size = numcol)) +
  geom_point(alpha=0.7,             # Allows the points to be see-through
             color ="#ac8405") +
  coord_flip()+                     # Flips the coordinate plane
  scale_size(range = c(1.4, 13), name="Number of Colonies (per thousand)") +
  theme(legend.position="bottom") +   # Places the legend at the bottom
  labs(x = "Yield per Colony",        # Adds nice titles to the plot
       y = "Price per Pound (lb.)") +
  transition_states(year,             # Animates the plot by year
     transition_length = 10, 
     state_length = 10)+
  ease_aes("cubic-in-out") +          # Edits the transition between points moving
  ggtitle('Honey Production in the United States',   # Adds title and subtitle to the animation
          subtitle = 'Year: {closest_state}')

#anim_save(here("Good Plot & Bad Plot", "Output", "Goodplot.gif"))
# Saves the animation
```

## Why is This Plot so Much *better*?

* Has a story to tell with the data (animated by year)
* Clearer data points
* Neater labels
* No unecessary images or colors to distract from the plot
* A more useful legend
