---
title: "2023-04-20 - Factors Homework"
author: "Mikayla Kerchen"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
```

## Load Data

```{r}
IntTidal_Data <- read_csv(here("Week_12", "Data", "intertidaldata.csv"))

View(IntTidal_Data)
```

## Changing Column Names 

I am changing the column names to be more clean. I also added percent and count to some columns to specify what the numbers represent.
```{r}
colnames(IntTidal_Data) <- c("site", "transect", "quadrat", "bare_rock_percent", "algae_percent", "mussels_percent", "small_barnacles_percent", "large_barnacles_percent", "gooseneck_barnacles_percent", "anemone_percent", "whelks_count", "crabs_count", "stars_count")
```


## Fixing the Character Data

I removed the "1", ".", and extra white space from the **quadrat** column. I renamed the new data frame as *IntTidal_Data_Fixed*.
```{r}

IntTidal_Data_Fixed <- IntTidal_Data %>%
  mutate(quadrat = str_replace_all(quadrat, "[0-9]|\\.", ""), # Removes the extra "1" and "." from the 'Quadrat' column
         quadrat = str_trim(quadrat))  # Removes white space

glimpse(IntTidal_Data_Fixed)
```

# Changing Character Columns to a Factor

I changed the character columns into a factor by using the **mutate()** and **factor()** functions. I also reordered the levels of the *quadrat* column to go from **Low** to **Med** to **High**. I renamed this data frame as *IntTidal_Data_New*.
```{r}
IntTidal_Data_New <- IntTidal_Data_Fixed %>% # Making a new Data Frame for the factors
  mutate(quadrat = factor(quadrat, levels = c("Low", "Mid", "High"))) %>%  # Making the column 'Quadrat' a factor and ordering the levels from Low to Mid to High
  mutate(site = factor(site))  # Making the column 'Site' a factor

glimpse(IntTidal_Data_New)
```

# Making a Plot and Reordering the Factor 

I used the new data frame to make a column plot. I first mutated the *algae_percent* column by 100 so the numbers would show up as percentages on the plot. I used *fct_reorder* to reorder the tide levels so they would show from **Low** to **Med** to **High**.  
```{r}
IntTidal_Data_New %>%
  mutate(algae_percent = algae_percent/100) %>%
  ggplot(aes(x = fct_reorder(quadrat, algae_percent, .desc = TRUE), # Reorders the factor of Quadrat by Algae in descending order (low, mid, high)
             y = algae_percent,
             fill = site))+ 
  geom_col() +   # Makes a column plot
  scale_fill_viridis_d()+    # Color blind friendly palette 
  labs(x = "Quadrat",
       y = "Algae (%)",   # Adds labels to the plot
       title = "Percentage of Algae per Quadrat",
       subtitle = "By Site")+
  theme(plot.title = element_text(size = 16,      # Changes the text size, color, face, and adjustment on the plot.
                                  color = "black",
                                  face = 'bold',
                                  hjust = 0.5),
        plot.subtitle = element_text(size = 14,
                                     color = "black",
                                     face = 'italic',
                                     hjust = 0.5),
        axis.title = element_text(size = 12,
                                  color = "black"),
        legend.title = element_text(size = 12,
                                   color = "black"),
        axis.text = element_text(size = 9,
                                 color = "black"))
```

